HPC--101\\Onboarding

### 2016-01-22 hpc_101/paper.tex
Defined Job Schedulers and last slides reordering

\begin{frame}
	\frametitle{What is a Job Scheduler?}
	Basic features expected of a job scheduler include:
	\begin{itemize}\footnotesize
        \item The capability to control and prioritize the execution order of unrelated jobs
        \item Allocate exclusive and/or non-exclusive access to resources to users for some duration of time so they can perform work
	\item Provides a framework for starting, executing, and monitoring work on the set of allocated resources
	\item Arbitrate contention for resources by managing a queue of pending work
	\end{itemize}
	\bigskip
	For the {\craycs}, we utilize the \textbf{S}imple \textbf{L}inux \textbf{U}tility \textbf{R}esource \textbf{M}anager~\\ or simply known as the \emph{SLURM scheduler}
	\numlessfootnotetxt{\tiny \url{https://en.wikipedia.org/wiki/Slurm_Workload_Manager}}
	\numlessfootnotetxt{\tiny \url{http://slurm.schedmd.com/slurm.html}}
\end{frame}

@@

\begin{frame}
\frametitle{SLURM commands}\footnotesize
SLURM has a series of commands, each of which allow users to interact with the job scheduler
\begin{itemize}\tiny
	\item \emph{\textbf{srun}} --  Used to submit a job for execution or initiate job steps in real time
	\item \emph{\textbf{srun.x11}} -- Used to submit an interactive job with x11 support
	\item \emph{\textbf{sbatch}} -- Used to submit a job script for later execution. The script could contain one or more srun commands
	\item \emph{\textbf{scancel}} -- Used to cancel a pending or running job or job step. It can also be used to send an arbitrary signal to all processes associated with a running job or job step
	\item \emph{\textbf{sinfo}} -- Reports the state of partitions and nodes managed by Slurm. It has a wide variety of filtering, sorting, and formatting options
	\item \emph{\textbf{squeue}} -- Reports the state of jobs or job steps
	\item \emph{\textbf{sacct}} -- Used to report job or job step accounting information about active or completed jobs
	\item \emph{\textbf{scontrol}} -- The administrative tool used to view and/or modify Slurm state. Note that many scontrol commands can only be executed as user root
\end{itemize}
\begin{itemize}
	\item[--] Examples usage of the SLURM commands can be seen on schedmd's \href{http://slurm.schedmd.com/quickstart.html}{quickstart}
	\item[--] Each command should have a `man' page, or displays help when the -h flag is used
\end{itemize}
\numlessfootnotetxt{\tiny \url{http://slurm.schedmd.com/quickstart.html}}
\end{frame}

@@

\section{Frequently Asked Questions}
\begin{frame}
\frametitle{FAQ}
\begin{itemize}\footnotesize
\item Are files on the cluster backed up?
  \begin{itemize}\tiny
  \item \textbf{Answer:} \textbf{NO!}  User files on the cluster \textbf{\emph{are not backed up}}.  It is up to you as the user to validate and maintain your own backups.  The {\citeam} takes no responsibility for any data that is lost due to human or mechanical error.  
  \end{itemize}

>>>>

\begin{frame}
  \frametitle{Job Schedulers}
  \begin{block}{Purpose}To control and prioritize the execution order of unrelated jobs\end{block}
	Basic features expected of a job scheduler:
	\begin{itemize}\footnotesize
        \item Provides a user interface for users to request resources and monitor work 
        \item Allocates access to resources for the requested duration of time
	\item Starts, monitors and terminates work on allocated resources
	\item Arbitrates contention for resources by managing queues of pending work
	\end{itemize}
	\bigskip
        The {\craycs} uses the \textbf{S}imple \textbf{L}inux \textbf{U}tility for \textbf{R}esource \textbf{M}anagement~\\ or simply known as the \emph{SLURM scheduler}
	\numlessfootnotetxt{\tiny \url{https://en.wikipedia.org/wiki/Slurm_Workload_Manager}}
	\numlessfootnotetxt{\tiny \url{http://slurm.schedmd.com/slurm.html}}
\end{frame}

@@

\begin{frame}
\frametitle{SLURM commands}\footnotesize
SLURM has a series of commands, each of which allow users to interact with the job scheduler
\begin{itemize}\tiny
	\item \emph{\textbf{srun}} --  Used to submit a job for execution or initiate job steps in real time
	\item \emph{\textbf{srun.x11}} -- Used to submit an interactive job with X11 support
	\item \emph{\textbf{sbatch}} -- Used to submit a job script for later execution. The script could contain one or more srun commands
	\item \emph{\textbf{scancel}} -- Used to cancel a pending or running job or job step. It can also be used to send an arbitrary signal to all processes associated with a running job or job step
	\item \emph{\textbf{sinfo}} -- Reports the state of partitions and nodes managed by Slurm. It has a wide variety of filtering, sorting, and formatting options
	\item \emph{\textbf{squeue}} -- Reports the state of jobs or job steps
	\item \emph{\textbf{sacct}} -- Used to report job or job step accounting information about active or completed jobs
	\item \emph{\textbf{scontrol}} -- The administrative tool used to view and/or modify Slurm state. Note that many scontrol commands can only be executed as user root
\end{itemize}
\begin{itemize}
	\item[--] Examples usage of the SLURM commands can be seen on schedmd's \href{http://slurm.schedmd.com/quickstart.html}{quickstart}
	\item[--] Each command should have a `man' page, or displays help when the -h flag is used
\end{itemize}
\numlessfootnotetxt{\tiny \url{http://slurm.schedmd.com/quickstart.html}}
\end{frame}

@@

%\section{Frequently Asked Questions}
\begin{frame}
\frametitle{FAQ}
\begin{itemize}\footnotesize
\item Are files on the cluster backed up?
  \begin{itemize}\tiny
  \item \textbf{Answer:} \textbf{NO!}  User files on the cluster \textbf{\emph{are not backed up}}.  It is up to you as the user to validate and maintain your own backups.  The {\citeam} takes no responsibility for any data that is lost due to human or mechanical error.  
  \end{itemize}
